### 2020-10-02 readme.Rmd
updating readme

## ppmData is temporary R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.

>>>>

## ppmData is an R package that can be used to set up a quadrature scheme for multiple species point processes modelling and could be used in [ecomix](https://github.com/skiptoniam/ecomix).
